---
title: "Crown width vs. DBH"
author: "Masatoshi Katabuchi"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 12pt
format:
  html:
    theme: coderpro
    toc: true
    toc-depth: 2
    number-sections: true
    smooth-scroll: true
    standalone: true
    embed-resources: true
---

```{r global_options, include=FALSE}
library(knitr)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE,
  cache = FALSE,
  fig.align = "center",
  fig.show = "hold"
)
```

I will explain a MLE example for crown width vs. DBH using a power-law model.

# Load the packages
```{r}
library(tidyverse)
library(here)
```

# Data preparation

I prepared `tallo_cleaned.csv` withouth wood density but with other iformation like laitiude and family.
We may need these information later.
For example, we can use faimly or biomes as random effects if needed.

```{r}
tallo_df <- read_csv(here("data/tallo_cleaned.csv"))
tallo_df
```

I also prepared wood density data for each species (`wd.csv`)
It's better to have species-based data (i.e., number of species = number of rows) for the analysis.

```{r}
wd_df <- read_csv(here("data/wd.csv"))
wd_df <- wd_df |>
  mutate(wd_s = scale(wd) |> as.numeric())
wd_df
```

You can easily join these two dataframes by `sp` (species name) before the analysis.

```{r}
tallo_wd <- left_join(tallo_df, wd_df, by = "sp")
tallo_wd
```

# Example for *C* vs. *D*

For tree *i* and species *j*, we assume that crown width ($C$) and DBH ($D$) has a power-law relationship :
$$
\text{ln}C_{i} \sim N(\alpha_j + \beta_j \text{ln}D_{i})
$$ {#eq-cd}

and species-level varaition can be explaiend by wood density ($\rho$):
$$
\begin{split}
\text{ln}C_{i} &= \alpha_{j} + \beta_{j}\text{ln}D_{i} + \epsilon_{i} \\
\alpha_j &= \gamma_{0}^{(\alpha)} + \gamma_{1}^{(\alpha)}\rho_{j} + \eta_{j}^{(\alpha)} \\
\beta_j &= \gamma_{0}^{(\beta)} + \gamma_{1}^{(\beta)}\rho_{j} +\eta_{j}^{(\beta)}.
\end{split}
$$ {#eq-wd_lmm}

To use `lme4::lmer`, we need to re-express the model (@eq-wd_lmm) as:

$$
\text{ln}C_{i} =
(\gamma_{0}^{(\alpha)} + \gamma_{1}^{(\alpha)}\rho_{j} + \eta_{j}^{(\alpha)})
 + (\gamma_{0}^{(\beta)} + \gamma_{1}^{(\beta)}\rho_{j} +\eta_{j}^{(\beta)})\text{ln}D_j + \epsilon_{i}.
$$ {#eq-wd_lmm_re}


We define new variables (
$a_j = \gamma_{0}^{(\alpha)} + \eta_{j}^{(\alpha)}$,
$b_j = \gamma_{0}^{(\beta)} + \eta_{j}^{(\beta)}$,
$c = \gamma_{1}^{(\alpha)}$, and
$d = \gamma_{1}^{(\beta)}$),
and we can further re-express the above model (@eq-wd_lmm_re) as:

$$
\text{ln}C_{i}= a_j + b_j \text{ln}D_{i} + c \rho_{j} + d \text{ln}D_{i} \times \rho_{j} + \epsilon_{i}.
$$ {#eq-lmer}

The correspoding R code looks like the following:

```{r, eval=FALSE}
lme4::lmer(log(cr) ~ log(dbh) + wd_s + log(dbh):wd_s + (1 + log(dbh) | sp), ...)
```

In this code, `(1 + log(dbh) | sp)` indiates varying intercepts ($a_j$) and slopes ($b_j$) for each species.
If you use `(1 | sp)`, this indicats only varying intercepts ($a_j$).

Note that:

- $a_j$ and $b_j$ are vectors of lenght $J$ (number of species).
- $c$ and $d$ are sclars (single values).

```{r}
fit_cd_power <- lme4::lmer(log(cr) ~ log(dbh) + wd_s + log(dbh):wd_s + (1 + log(dbh) | sp), data = tallo_wd)
summary(fit_cd_power)
```

The t-value for wd_s is relatively large (> 3), which indicates $c = \gamma_{1}^{(\alpha)}$ is (probably) significant.
This pattern was not that clear in Martínez Cano's paper.
On the other hand, $d = \gamma_{1}^{(\beta)}$ doesn't seem to be significant.

# Next

Power-law models with `lme4` are just preliminary analysis.
We also want to use gMM and Weibull, which requrie other R packages.
It will be more straightforward to use `stan` for all the models.

- Write **equations** for stan codes for:
  - power-law
  - gMM
  - Weibull

- Write stan codes for:
  - power-law
  - gMM
  - Weibull

- Write simple stan codes for simple data.

- Create dummy data for your stan codes.

#  Liner models with dummy data example

## Dummy data
$$
y_i \sim N(\beta_0 + \beta_1 x_i, \sigma)
$$ {#eq-lm}

where $\beta_0$ = 1.2, $\beta_1$ = -0.8, $\sigma$ = 0.5, and the number of samples (n) is 100.

```{r}
set.seed(123)
n <- 100
beta0 <- 1.2
beta1 <- -0.8
sigma <- 0.5

x <- rnorm(n)
mu <- beta0 + beta1 * x
y <- rnorm(n, mu, sigma)
plot(x, y)
```

### Matrix Operations

In practice, we use matrix operations to handle computations:

```{r}
x_mat <- cbind(1, x)
mu2 <- x_mat %*% c(beta0, beta1)

# mu and mu2 are expected to be equal
testthat::expect_equal(mu, as.numeric(mu2))
```

## Linear Regression (MLE Approach)

```{r}
fit <- lm(y ~ x)
summary(fit)
```

## Bayesian Analysis with Stan

### Stan model

The Stan model code is stored in `stan/lm_example.stan`:

```{stan, size="small", file="../stan/lm_example.stan", echo=TRUE, eval=FALSE, output.var="hoge"}
```

As you can see, the stan code looks like how the dummy data was generated.
This is why it is a good practice to write both stan code and code to generate dummy data.
It helps you to understand the model and to debug the code.

Summary of posteriors:

<!-- ```{r}
# targets::tar_read(fit0_summary_lm_example)
withr::with_dir(rprojroot::find_root('_targets.R'),
    targets::tar_read(fit0_summary_lm_example))
```
 -->
